\documentclass{slides}
\usepackage{url}
\title{Advanced Topics in Systems Administration -- Introduction}
\author{Steven L. Jenkins}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}

\begin{document}

\maketitle

\slide{Introduction}

\bi
\item Placement with 4417
\item Syllabus
\item Policies
\item Material
\ei

\slide{Placement with 4417}

SAGE: \url{http://sageweb.sage.org/jobs/thefield/jobs-descriptions.html}

The purpose of 4417 is to bring students up to the 
Intermediate/Advanced level of SAGE.  The purpose of this
course is to bring people to the Senior level.  There are two
primary ways to reach this level:

\bi
\item Technical depth
\item Management ability
\ei

In this course, we will cover both.  This will cause you
stress as most students view themselves as one or the other.

\slide{Syllabus}

Blackboard: \url{http://online.etsu.edu/}

Note in particular:

\bi
\item Coverage parallels that of 4417
\item Cross-platform is more important
\item Automation is more important
\item Scale
\ei

\slide{Policies}

\bi
\item Time
\item Readings
\item Grading
\item Grade scale: standard
\ei

\slide{Time}

The usual formula for time is 3 hours outside of class for every hour
in lecture.  Using that formula, I envision the following breakdown:

\begin{tabular}{c|c}
Primary Reading & 1 hour\\
Additional Readings & 1 hour\\
Internet searches & 1 hour\\
Projects/assignments & 6 hours\\
\hline
Total & 9 hours
\end{tabular}


\slide{Readings}

\bi
\item Expect to read 100 pages per week, minimum, but note
that none of our texts are as dense as normal textbooks.
\item Required text: Limoncelli and Hogan
\item Recommended texts: only if you find you need more
written material.  Much of that is freely-available on the Internet.
\item Papers, as assigned (expect 2-3 per week, but will vary)
\ei

\slide{Grading}

\bi
\item Projects 50\%
\item Exams    30\%
\item Assignments 20\%
\item Quizzes -- only if needed (e.g., possibly 20\%, bringing
everything up to 120\%)
\ei

\slide{Exams}

These are most likely to be essay:

\bi
\item Mid-term 15\%
\item Final (cumulative) 15\%
\ei

\slide{Assignments}

\bi
\item \LaTeX{} lecture notes (one per person)
\item Present papers (2-3 per person)
\item Short, exploratory assignments (as a class: expect 3-5 of these)
\ei

\slide{Quizzes}

Unnannounced quizzes will be over the reading material if I determine 
that adequate preparation is not being done.

Corollary: you can make yourself extremely unpopular if your lack of
preparation causes the entire class to start having quizzes.

\slide{Projects}

There are three categories of projects:

\bd
\item[Small: 1 point] 10-20 hours
\item[Large: 2 points] 20-30 hours
\item[Group: 1 point] 30-50 hours total
\ed

Each person will be required to do at least one group project, and your
total points from projects should be 8.

Suggestions/ideas for projects are on the following slides.  Note that 
these are only suggestions.  You must confirm with the instructor before
beginning any project as to its scope and availability.

\slide{Small Projects}

Install, configure, and write up a short presentation on your 
experiences with:

\begin{tabular}{|c||rrr|}
\hline
OS's 	& OpenBSD 	& FreeBSD	& Solaris \\
\hline
Apps 	& CVS 		& Tripwire 	& Cyrus \\
		& iPlanet	& LDAP		& bugzilla \\
\hline
Other		& Build cables	& WW lab work	& \\
\hline
\end{tabular}

\slide{Large Projects}

\begin{tabular}{ll}
Write HOW-TO		& Install Coda \\
Product eval paper 	& Configure cfengine\\
Performance analysis	& Monitoring	\\
Enhance OS Project & Build honeypot \\
Design a new tool & Build that new tool \\
\end{tabular}

\slide{Group Projects}

\begin{tabular}{rr}
Build firewall for WW & Make WW reconfigurable \\
XP Kickstart? & Configure Chord for WW\\
\end{tabular}

\slide{Project Grading}

\bi
\item Grades will be on a percentage basis
\item All projects are to be presented in class (3 slides max)
\item You must have 3 points completed by March 5, or you will
	receive an automatic zero for the rest of your projects
\item No projects submitted after April 17
\item At least one large project per person
\item At least one group project per person
\item At least one project must result in a paper of
	sufficient size and scope for a submission to a journal
	or conference
\item Size (small, large, group) is negotiable; however, negotiation
	must be done before beginning the project!
\item Part of the grade will be on originality: note that if I 
	have to suggest a topic for you, then the topic is
	not original.
\ei

\end{document}
