\documentclass{slides}
\usepackage{url}
\title{Advanced Topics in Systems Administration -- Lecture 9}
\author{Steven L. Jenkins}
\date{March 11, 2003}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}

\begin{document}

\maketitle

\slide{Agenda}

\bi
\item Distribute exam
\item Chapter 19: Email
\item Mail group work teams
\item Chapter 20: Printing
\item Chapter 21: Backup and Restore
\item Chapter 22: Remote Access
\ei

\slide{Exam}

\bi
\item Due April 2, start of class (7pm)
\item Hardcopies only
\item My estimate is 10 hours of time, assuming you do all your
  work in a word processor.
\item I'll use Blackboard's discussion board (I've removed anonymous posting,
but enabled editing or removing your own posts)
\ei

\slide{Mail Group Teams}

\bi
\item Microsoft: Robert*, Sai, Adam, Kao-Yee, Judith
\item Open Source 1: Rick, Lingling, Trey, David, Vamshi*
\item Open Source 2: Steve, Todd, Amanda, Narsimha, Mario, Gunter
\ei

Note that Robert and Vamshi may opt out of the project.  If Robert opts
out, then Gunter will move to the first group.

\slide{Mail Assignment: Overview}

Set up the following:

\bi
\item At least one MUA
\item Mail store
\item MTA from MUA to store
\item MTA from MTA to other groups 
\ei

An implicit part of the assignment is to work out a good naming scheme
for email addressing (as well as enough DNS configuration to talk
between the clients and servers -- hardcoding DNS is fine).  Each person 
in your group must have an email 
account.  You may find it convenient to leverage SAI's LDAP project 
so that you can more easily handle mail routing. 

\slide{Mail Assignment: Microsoft}

\bi
\item Name: ms.example.org
\item MUA: Outlook (with POP, IMAP, and MAPI; must use SSL)
\item MUA: OWA (Outlook Web Access)
\item MTA and Mail store: Exchange (any version -- the beta of Exchange
  2003 is available from Microsoft for free; Robert also has a copy of
  Exchange 2000 under the MSDNAA).  
\item MTA to other groups: Exchange
\ei

\slide{Mail Assignment: OS 1}

\bi
\item Name: os1.example.org
\item MUA: Ximian Evolution (must configure POP and IMAP)
\item MUA: Web client of your choice
\item MTA: sendmail
\item Mail store: Cyrus IMAP
\item MTA to other groups: sendmail
\ei

Note: if Gunter moves to group one, then the requirement for the second
MUA is dropped.

\slide{Mail Assignment: OS 2}

\bi
\item Name: os2.example.org
\item MUA: PINE
\item MTA: qmail (or PostFix)
\item Mail store: UW IMAP
\item MTA to other groups: qmail (or PostFix)
\ei

\slide{March 25 Agenda}

\bi
\item Exam due April 2; mail work due April 9
\item \emph{The Depot: A Framework for Sharing Software Installation
  Across Organizational and UNIX Platform Boundaries}, by
  Manheimer, et al, in LISA IV (1990).  Try Google or Citeseer.
\item PSNA Chapter 23: Software Depot Service
\item PSNA Chapter 24: Monitoring
\item PSNA Chapter 25: Organizational Structures
\item PSNA Chapter 26: Perception and Visibility
\ei

\end{document}
