\documentclass{slides}
\usepackage{url}
\title{Advanced Topics in Systems Administration -- Lecture 2}
\author{Steven L. Jenkins}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}

\begin{document}

\maketitle

\slide{Agenda}

\bi
\item Discuss papers assigned
\item PSNA Chapter 2
\item PSNA Chapter 3
\item PSNA Chapter 4
\item Assign more readings
\ei

\slide{Evard}

This article was written in 1997.  Let's explore how (if) the 
world has changed.

\bi
\item He asserts systems administration is growing more 
	complex.  Agree or disagree?  Why?

\item What are the Windows equivalents of {\tt /etc/passwd},
	{\tt crontab}, and {\tt /etc/inetd.conf}?

\item Assignment: What are the Windows equivalents of Figure 2?  

\item \emph{The real killer for systems administrators is change.}

\item Theory question: is there some way to make this social
	science survey into hard science?  
\ei

\slide{Fulmer and Levine}

\bi
\item What is your cost estimate of this solution?
\item How well will this solution scale to newer releases of Windows?
\item How well will this solution scale to a more diverse hardware
	environment?
\ei


\slide{Gomberg, Evard, Stacey}

\bi
\item To read: Depot (Colyer \& Wong, 1992)
\item Software continuum
\item Classes of machines, not a single build
\item Reliance on Microsoft-sanctioned methods
\ei

\slide{Gomberg, Evard, Stacey (2)}

\bi
\item Packaging costs
	\bi
		\item unattended install option
		\item additional tools (e.g., IE and Office resource kits)
		\item VB app that clicks the right place at right time
	\ei
\item They don't have many complaints about SMS
\ei

Sidebar: Files, hard links and symbolic links

\slide{Heiss}

\bi
\item {\tt rpc.bootparamd} versus DHCP
\item 600 machines upgraded in 6 months -- too slow
\item Failure rate of 30\%
\ei

\slide{Heiss (2)}

\bi
\item More error checking
\item Note choice of tool (Perl, not {\tt /bin/sh})
\item Infrastructure cleanup (e.g., \emph{rogue} {\tt rarpd} servers)
\item tell 600 machines do reboot (scale)
\item real-time status page
\item Note: author has a TODO list on his website
\ei

\slide{Martin and Brooks}

\bi
\item \emph{DLL Hell}
\item {\tt sysdiff} (not in XP, but see \\
	\url{http://www.microsoft.com/oem})
\item shared file conflict resolution
\item {\tt jacal} project (on Sourceforge) (dead?)
\ei

\slide{Market Economics}

\bi
\item Exercise: estimate the market value of Jacal
\item \url{http://www.altiris.com}
\item \url{http://www.powerquest.com}
\item How much would it cost to enhance to marketable
	quality?
\item How many copies at what price would need to
	be sold to cover that cost?
\item Should Brooks and Martin quit their day jobs and
	create a start-up?
\ei

\slide{Kickstart}

\slide{Ressman and Valdess[2000]}

\bi
\item The year is now 2000
\item Unix-only solution
\item smart clients \& dumb server solution
\item No centralized file systems
\item Three parts: 
	\bi
	\item software distribution
	\item patch distribution
	\item configuration management
	\ei
\ei

\slide{Ressman and Valdes[2000] (2)}

\bi
\item software distribution: use existing, multi-platform package format 
	(RPM) on top of FTP
\item patch distribution: leverage FTP (Are there better solutions today?)
\item configuration management: cfengine
\item storage: 100 programs $\times$ 100 machines $=$ 10,000 entries, which
	implies a relational database (MySQL)
\item programming language: Perl
\ei

\slide{Ressman and Valdes[2000] (3)}

Does RedHat network serve the same function as the system they built?

\slide{Beck[1999]}

\bi
\item Is this system necessary?
\item How much did this cost?
\item How much would this cost at ETSU?
\item How much is it worth?
\ei

\slide{Valian[1999]}

\bi
\item Is this system necessary?
\item How much did this cost?
\item How much would this cost at ETSU?
\item How much is it worth?
\ei

\slide{Random project ideas}

\bi
\item
Survey the LISA papers, build a classification system, and see how the
topics over the years have changed, if at all.  For example, is there
any trend in papers on building systems?  Take Burgess' paper on the
Theory of Systems Administration and see if anything interesting is
there.

\item
I have a pet software project (or two) that needs to be put into RPM.

\ei

\slide{Readings for next time}

\bi
\item Athena (\emph{Network Services in the Athena Environment})
\item Vincent/Acropolis (\url{http://linux.ait.iastate.edu/pub/doc/development/ISU_Big_Picture.txt})
\item Aurora (\url{http://www.usenix.org/publications/library/proceedings/lisa95/gittler.html})
\item PSNA Chapters 5-9
\ei

\end{document}
