\documentclass{exam}
\usepackage[dvips]{graphicx}
\usepackage{comment}
%\linespread{1.3} % for one and a half
%\linespread{1.6} % for double-spacing
\newcommand{\myq}{\question[1]}
\addpoints
\begin{document}
%\maketitle
{\large CS 5360 Mid-term 2003}\\
%\vspace{0.2in}
\hbox to \textwidth{\large Name:\enspace\hrulefill}
\vspace{0.1in}

This exam has \numquestions{} questions for a total of \numpoints{} points.

\begin{questions}

\question[100]

\section*{Introduction}

Congratulations!  You have just been hired by ABC Company, which is looking
to expand.  You have been asked to provide Systems Administration
consulting directly to the CEO, who wants you to look over the company's
business plan and make suggestions about the company's IT infrastructure
needs.  Your presentation should both educate the CEO about the basic
options, as well as make recommendations.  In addition, you are asked 
to prepare training materials
suitable for the setup of the new IT staff.

Note that the company has contracted for multiple presentations -- sharing
of presentation materials across the consultants is forbidden by contract.
\emph{Translation: all work should be done by individuals with no discussion
of the exam, per the Code of Conduct.}

For your reference, I have included the chapter titles of the first
14 chapters of PSNA:

\begin{enumerate}
\item Desktops
\item Servers
\item Services
\item Debugging
\item Fixing Things Once
\item Namespaces
\item Security Policy
\item Disaster Recover and Data Integrity
\item Ethics
\item Change Management and Revision Control
\item Server upgrades
\item Maintenance Windows
\item Service Conversions
\item Centralization and Decentralization
\end{enumerate}

\section*{Business Models}

\begin{enumerate}
\item Large company with 5000 employees on a 3-building campus handling 
  the back-end of an
  e-commerce site.  There is an in-house development team of 10 developers,
  and the full-time, permanant IT staff for internal needs should have no 
  more than an additional 20 people.  You do not need to consider
  the Help Desk for external users.  Note that each person in the
  company has a desktop PC.  There are 4 servers for development, and
  4 servers for production use by the e-commerce site.  
  Other servers (and services) need to  be specified by you.
\item Small engineering company with 200 employees, 150 of which are
  developers (on both Windows and Unix platforms), 30 of which are 
  sales \& marketing, with the final
  20 being management.  The company is heavily influenced by Extreme
  Programming and has broken up the developers into 20 small 
  departments with very differing needs.  You will need to make a 
  recommendation for the
  size of the IT team in addition to the other requirements.  Each
  engineer has 2 machines on her desk: one running Windows and one
  running either Solaris, FreeBSD, or Linux (you can assume roughly
  $1/3$ are running each platform).  
\item Small university of 1000 students, 50 faculty, and 
  20 administrative staff (including 5 IT).  Each faculty and staff
  member has a desktop PC, but no students have individual machines: they
  share the use of 4 labs with 50 machines each that are open 24 hours.
  
\end{enumerate}

\section*{Deliverables}

All materials should be suitable for presentation to an appropriate audience.

\begin{itemize}
\item An introduction to the material, describing which  of the first
  14 chapters in
  \emph{The Practice of System and Network Administration} are important
  for the CEO and which are important for the IT staff.
\item A slide presentation for the CEO, covering the appropriate items, 
  with appendices if necessary.
\item Materials for the IT staff in whatever form you think most 
  appropriate for training and reference.
\end{itemize}

\section*{Hints}

You will need to answer at the appropriate level.  For example, on the
chapter on desktops, you do not need to go to a vendor's website and get
prices of hardware (you aren't being asked for cost information on this
assignment).  Instead, you need to consider the company, it's needs, and
the size of the IT staff to determine what the right model for computing
would be for the company.  In your presentation, you will need to educate
your audience about the basic choices that need to be made, and show them
your recommendations (clearly explaining why you have made that choice).

While you are not allowed to discuss this with any other student, you are
free to ask me questions.  I would prefer for you to email me questions
directly, and I will post questions and answers to the discussion board
on Blackboard.

Also, you are free to use materials from elsewhere on this exam, in 
particular, use this exam as an opportunity to examine others' policy
documents and put together a portfolio of IT policies.  You should also
use this opportunity to put together a sample runbook (or 
\emph{Flight Director's Handbook} of large changes).

\end{questions}

\end{document}

