\documentclass{slides}
\usepackage{url}
\title{The Practice of System and Network Administration: Chapter 4}
\author{Steven L. Jenkins}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\assignment}[1]{{\bf Idea: } #1 }

\begin{document}

%\maketitle

\slide{PSNA Chapter 4: Debugging}

\begin{quotation}
Debugging is not simply making a change that fixes a problem.  That's
the easy part.
\end{quotation}

So what is debugging?

\slide{Goodbye to the problem}

How can you make the problem disappear for good?

\slide{The Basics}

\bi
\item Learn the customer's failed goal (problem).
\item Find the problem's cause and fix it.
\item Have the right tools.
\ei

\slide{The Problem}

\bi
\item Be polite.
\item A reported outcome is about an expected outcome not happening.
\item Understand the limits of customer's assistance.
\ei

\slide{The cause and fix}

\bi
\item Workarounds are bad
\item Reboots (and restarts) are a sign of a lazy SA
\item Process of elimination
\item Successive refinement (\emph{follow-the-path})
\item What changes were made recently
\item Correct the root cause
\ei

\slide{Tools}

\bi
\item Have tools
\item Know how things work so you can use the tools
\item Know how to build tools (anecdote)
\item Vendor-supplied tools and feedback (anecdote)
\ei

\slide{Conclusion}

End-to-end understanding: gurus and architects

\end{document}
