\documentclass{slides}
\usepackage{url}
\title{PSNA Chapter 14: Centralization and Decentralization}
\author{Steven L. Jenkins}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\begin{document}

\slide{Centralization vs. Decentralization}

How do you decide how much centralization is appropriate?

This chapter seeks to help answer that question.

\slide{Background}

\emph{Centralization is an attempt to improve efficiency by \
reorganizing to take advantage of potential economies of scale.}

\emph{Decentralization is an attempt to improve speed and flexibility \
by reorganizing to increase local control and execution of a service.}

\slide{The Basics}

A theme in this section is to \emph{write down} (i.e., document)
what (and why) you are doing.

\bi
\item Understand your motivation for making the change
\item Know what specific problem you are solving
\item Centralize as much as makes sense for today, with an
  eye to the future
\item Greater centralization leads to greater need for
  decentralization
\item Consider Centralizing commodities
\ei

\slide{The Basics (cont.)}

\bi
\item Avoid unrealistic promises (both yours and others)
\item Use your best judgement
\item C/D is like deploying any other service
\item Listen to the customers
\item You only have one chance to make a good first impression
\item Listen to the customers, but remember that management has the control
\ei

\slide{Candidates for Centralization}

\bi
\item Management of distributed systems
\item Services onto fewer hosts
\item System Administration
\item Expertise
\item Infrastructure decisions
\ei

\slide{Why Decentralize?}

\bi
\item Trade efficiency for something more valuable
\item Control
\item Fault tolerance
\item Customized solution
\item Independence (protection) from central authorities
\item Diversity (biological)
\ei

\slide{Candidates for Decentralization}

\bi
\item Fault tolerance (small offices)
\item Customization
\item Meeting customers' needs
\ei

Don't fall into the trap of decentralization into many single points
of failure (SPOF).

\slide{Icing}

Cheap, fast, good (or reliable).  Pick two.

\bi
\item Consolidate purchasing (carrot, not stick)
\item Outsourcing
\ei

\end{document}
