\documentclass{slides}
\usepackage{url}
\title{The Practice of System and Network Administration: Chapter 3}
\author{Steven L. Jenkins}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}
\newcommand{\assignment}[1]{{\bf Idea: } #1 }

\begin{document}

\maketitle

\slide{Services}

\begin{quotation}
Services are what distinguish a structured computing environment that is 
managed by SAs from an environment where there are one or more stand-alone
computers
\end{quotation}

\slide{What services does ETSU offer?}

\bi
\item network connectivity
\item DNS
\item NT user account management
\item mail
\item printing
\item others?
\ei

\slide{What services would you like to be offered?}

\bi
\item ubiquitous file services
\item Web publishing
\item mailing lists
\item calendaring
\item other?
\ei

\slide{Service goals}

\bi
\item make the service reliable
\item scale the service
\item monitor the service
\item maintain the service
\item support the service
\ei

\slide{The Basics: what does the customer want?}

\bi
\item Who is the customer at ETSU?
\item What does the customer want?
\item What SLA does the customer expect?
\item What SLA is the customer paying for?
\ei

\slide{Discussion}

\begin{quotation}
A server should be as simple as possible.
\end{quotation}

versus

\begin{quotation}
All systems should be built the same.
\end{quotation}

\slide{Design Tips}

\bi
\item Simple, single-purpose systems
\item Fewer, larger systems 
\item Service names in configurations versus hostnames
\item Consider carefully the upgrade path (in versions, scale, and products)
\item Bad capacity planning makes a bad first impression
\item Don't forget the network:
	$T = (S_1 + C_1 + R_1) + \ldots + (S_n + C_n + R_n)$
\ei

\slide{Discussion 2}

\begin{quotation}
We have found great success through the use of open protocols 
and open architectures.
\end{quotation}

versus

\begin{quotation}
No one ever got fired for buying 
(\emph{IBM} in the 70's, \emph{Microsoft} in the 90's)
\end{quotation}

\end{document}
