\documentclass{slides}
\usepackage{url}
\title{PSNA Chapter 17: Data Centers}
\author{Steven L. Jenkins}
\newcommand{\bi}{\begin{itemize}}
\newcommand{\ei}{\end{itemize}}
\newcommand{\bd}{\begin{description}}
\newcommand{\ed}{\end{description}}
\newcommand{\be}{\begin{enumerate}}
\newcommand{\ee}{\end{enumerate}}

\begin{document}

\slide{Data Centers}

\emph{A data center is anywhere that you keep machines that are
shared resources and where your customers do not need physical access.}

\emph{The theory is that you put all your most important eggs in one basket
and then make sure it is a really good basket.}

Who is responsible for power and cooling?

\slide{Considerations}

\bi
\item location
\item flooring
\item racks
\item wiring
\item power
\item cooling
\ei

\slide{Considerations (cont.)}

\bi
\item fire supression
\item natural disasters
\item man-made disasters
\item duration (8-10 years)
\ei

\slide{Picking a Location}

\bi
\item lightning
\item earthquakes
\item floods
\item What does East Tennessee have?
\ei

\slide{Access}

\bi
\item To get to the building (legal issues and infrastructure)
\item To get in the building (delivery dock? wheelchair ramps?)
\item To get in the data center
\ei

\slide{Security}

\bi
\item Need-to-access basis only
\item Fewer hands implies fewer accidents
\item Don't use simple keys (ATT paper on mastering)
\item Proximity badges are nice
\item Biometrics if necessary (ethics?)
\ei

\slide{Power and Air}

\bi
\item Power and cooling max out at the same time
\item One ton cooling for every 5K sq feet
\item Humidity control can be important
\item Power regulator (smoothing spikes, brownouts)
\item Battery
\item Generator
\item ATS (Automatic Transfer Switch)
\item Monitor temperatures (note the plural!)
\ei

\slide{Power Distribution}

\bi
\item Over  vs. under
\item Overhead power less likely to get flooded
\item Raised floors require water sensors in floors
\item Real PDUs (Power Distribution Units) not cheap power strips
\item Dual-system reduces risks
\ei

\slide{Fire Supression}

\bi
\item Some systems can kill
\item Water?
\item $CO_2$
\item Other gases
\ei

\slide{Racks}

\bi
\item basic issues: selection and layout
\item number of posts, height, width, depth
\item airflow, strength, mounting options, wiretrays
\item dual, vertical PDUs
\item cable management is critical
\item consider freestanding equipment
\ei

\slide{Wiring}

\emph{The cost of prewiring is more than compensated for by the productivity
it affords.}

\bi
\item Neatness counts
\item Raised floors are risky
\item Prewire as much as possible
\item Color coding
\item Leave slack for working on systems
\item Separate data and power
\item Labeling
\ei

\slide{Miscellaneous}

\bi
\item Radios or wall phones
\item Console servers (KVM switches or serial)
\item Carts and/or workbenches
\item Tools and supplies -- parking spaces
\item Carts and trucks
\ei

\slide{Icing}

\bi
\item Greater redundancy
\item More space
\item Ideal datacenters
\ei

\end{document}
